AIR4children: Artificial Intelligence and Robotics for Children

### 2021-02-14 article/tex/submission.tex
spell checked

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspects for inclusion, accesibility, transparency, equity, fairness and participation and (b) to create a child-centre approach for AI and robotics.
We introduce the present current challenges and opportunities for a child-centre approach for AI and robotics. 
Similarly, we touch on open-sourced software and hardware technologigies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that air4children can work with as development of open-sourced software and hardware, open-sourced teaching material. 
Finally, we add conclusions and future work. 
\end{abstract}

@@

\section{Introduction} 
The scientific and techonlogical progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapdily moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
However, such pupport brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR avaible to under-represented communities.
In terms of a child-centered AIR, ...
Similarly, such technologies are unreaachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to make AIR avaiable to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accesibility. 
Additionally, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socieconomical backgrounds, developmental stages or learning abilitities.

For this work, section 2 review open source projects as a way to minise cost for hardware and software as the basis of the materal for air4children which is presented in section 3. 
Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.

\section{Open Source Software and Hardware for AI and Robotics}
In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative simple accesibilty to users were crucial to its success \cite{gaudeul2007}.
Then, in 1983 Richard Stallman, with the fustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto stating the fredom to run, study, copy, and make modifcation of software \cite{stallman1985}.
That said, such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S. Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed and many others \cite{brasseur2018}.
Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.

In the last decade, another wave of scientific inovation has been emerging in the field of AI due to open source software framewoks (e.g. pytorch, tensorflow, etc.) and places to distrute these (e.g. GitHub, gitlab, bitbucket) \cite{matelabs2017}
However, little has been seen accross the fields of AI and Robotics. 
For instance, OTTO DIY is an educational open source robot founded in 2016 by Camilo Parra, the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
With regards to Robotics, the JPL Open Source Rover, created by eingeerers at NASA and initially released in April 2018, is a good reference as it is designed with detialed instructiosn for contrutrions for high school students and beyond, and technical specifications, 3D models, ensmabled instructions are fully avaiable \cite{OSR:2018}.
Recently, engineers at NVIDIA in 2019, resleased nano JetBot as a affortable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}. 
That said, there is room to create platforms to create educational resources to teach AI and robotics, as pointed by JetBot, in a more affordable, educatianal and fun characteristcs.
Table~\ref{tab:opensourceprojects} summarises three open source projects with year of establisment and cost.

@@

\section{AIR4Children as a open source project}
Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therfore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customiseble and accesible tools for a child-centred AIR.

In a first phase, air4children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the particpants. 
This inital phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.

@@

\subsection{Open source hardware and software}
Adpoting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).

\subsection{Open teaching materials}
Considering teaching materials to be child-like oriented, air4children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for air4children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) \cite{bers2012, resnick1998}.
Similarly, Elkin et al. (2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adoped for air4children to reinforce the above Montesory skills \cite{tarik2017}.

%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learnig divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}

@@

\section{Conclusions and future work}
We introducted the term air4project as a project with the aim to tackle aspects for inclusion, accesibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
In this work, we also touched on the open source projects in AI and Robotics as a corner stone for air4children with the aim of minise cost of the materials and made customised eduational material.  
Similarly, it has been presented the three phases for air4children for piloting, impleting and refiningg workshops for children in the age range between 6 to 14. 
We also touched on the creation of curriclumns with Montesoty education, a non-traditional eduational approach to help young audienes to develiip skills such as think creatively with curisitty and open-minded as well as develop a have a sense of wonder and joy in learning.

For future plans, in the coming year, we will complete the first round of eduational material for a child-centre AI and robotics where pilots, workshops and showcases are part of the 2021 and 2022 agenda.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create a child-centre approach for AI and robotics.
We introduce the present current challenges and opportunities for a child-centre approach for AI and robotics. 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that air4children can work with as development of open-sourced software and hardware, open-sourced teaching material. 
Finally, we add conclusions and future work. 
\end{abstract}

@@

\section{Introduction} 
The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
However, such support brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
In terms of a child-centered AIR, ...
Similarly, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility. 
Additionally, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.

For this work, section 2 review open source projects as a way to minimise cost for hardware and software as the basis of the material for air4children which is presented in section 3. 
Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.

\section{Open Source Software and Hardware for AI and Robotics}
In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative simple accessibility to users were crucial to its success \cite{gaudeul2007}.
Then, in 1983 Richard Stallman, with the frustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto stating the freedom to run, study, copy, and make modification of software \cite{stallman1985}.
That said, such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S. Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed and many others \cite{brasseur2018}.
Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.

In the last decade, another wave of scientific innovation has been emerging in the field of AI due to open source software frameworks (e.g. pytorch, tensorflow, etc.) and places to distribute these (e.g. GitHub, gitlab, bitbucket) \cite{matelabs2017}
However, little has been seen accross the fields of AI and Robotics. 
For instance, OTTO DIY is an educational open source robot founded in 2016 by Camilo Parra, the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
With regards to Robotics, the JPL Open Source Rover, created by engineers at NASA and initially released in April 2018, is a good reference as it is designed with detailed instructions for constructions for high school students and beyond, and technical specifications, 3D models, assembly instructions are fully available \cite{OSR:2018}.
Recently, engineers at NVIDIA in 2019, released nano JetBot as a affordable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}. 
That said, there is room to create platforms to create educational resources to teach AI and robotics, as pointed by JetBot, in a more affordable, educational and fun characteristics.
Table~\ref{tab:opensourceprojects} summarises three open source projects with year of establishment and cost.

@@

\section{AIR4Children as a open source project}
Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therefore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customisable and accessible tools for a child-centred AIR.

In a first phase, air4children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the participants. 
This initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.

@@

\subsection{Open source hardware and software}
Adopting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).

\subsection{Open teaching materials}
Considering teaching materials to be child-like oriented, air4children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for air4children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) \cite{bers2012, resnick1998}.
Similarly, Elkin et al. (2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adopted for air4children to reinforce the above Montessori skills \cite{tarik2017}.

%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learning divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}

@@

\section{Conclusions and future work}
We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
In this work, we also touched on the open source projects in AI and Robotics as a corner stone for air4children with the aim of minimise cost of the materials and made customised educational material.  
Similarly, it has been presented the three phases for air4children for piloting, implementing and refining workshops for children in the age range between 6 to 14. 
We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills such as think creatively with curiosity and open-minded as well as develop a have a sense of wonder and joy in learning.

For future plans, in the coming year, we will complete the first round of educational material for a child-centre AI and robotics where pilots, workshops and showcases are part of the 2021 and 2022 agenda.
